---
title: "task04_script"
author: "Abby"
date: "January 27, 2017"
output: html_document
---
# Task 04 Geol 590 
# ggplot2 script

Load proper packages
```{r}
library(ggplot2)
library(tidyverse)
library(extrafont)
```

determine how many rows the diamonds data set has that comes with ggplot2
```{r}
nrow(diamonds)
```
There are 53940 rows in diamonds 

Use the following code to create a reproducible subset of diamonds. Explain each line of the code in words.

```{r}
set.seed(1410)
dsmall <- diamonds[sample(nrow(diamonds), 100), ]
```
set.seed(1410) sets the random number generator to start at 1410, if we had started at 10 it would start at 10. 
dsmall <- diamonds[sample(nrow(diamonds), 100), ] selects 100 random rows from the data table diamonds and returns a new smaller data frame. 

###create scatter plots using gglot
Use dsmall to create the following plots:
A scatterplot of y vs x, colored by z values and faceted by cut 

```{r cars}
dsmallplot <- ggplot(dsmall,aes( x = x, y = y , colour = z))+
  geom_point()+
  facet_wrap(~cut)
print(dsmallplot)
```
A scatterplot of price vs carat, colored by cut and smoothed (using the "lm" method, without standard error bars)
```{r}
pricecarat <- ggplot(dsmall, aes( x = price, y = carat, color = cut))+
  geom_point()+
  geom_smooth( method = "lm", se = FALSE)
print(pricecarat)
```

A density plot of carat, faceted and colored by clarity
```{r}
densityplot <-ggplot(dsmall, aes(carat, color = clarity))+
  geom_density()+
  facet_wrap(~clarity)
print(densityplot)
```
A boxplot of price as a function of cut 
```{r}
box <- ggplot(dsmall, aes( x = cut, y = price))+
  geom_boxplot()
print(box)
```

A scatterplot of y versus x. The points should be red (colour = "red"), the color of the smoothing line should be blue (colour = "blue"), and the line should be dashed with fat dashes (linetype=2). The x and y labels should be set manually as well. The trickiest part of this may be to figure out where colour = "red" etc should go in the code. Think about mapped vs static aesthetic values.
```{r}
xycolor <- ggplot(dsmall, aes(x = x, y = y))+
  geom_point(color = "red")+
  geom_smooth(method = "lm", se = FALSE, color = "blue", linetype =2)
print(xycolor)
```
##Ugly Plot Contest 
Make the worst plot you possibly can in ggplot2. This plot should be awful in two independent respects: * It should represent the data misleadingly (this can sometimes be difficult with ggplot2, but be creative) * It should be as ugly as possible. (theme will be helpful here.) **Print this plot out and bring it in on Friday. We'll make a gallery of bad plots and the 'winner' will get a prize.

```{r}
set.seed(1410)
datasmall <- diamonds[sample(nrow(diamonds), 2500), ]

uglyplot<-ggplot(datasmall, aes(x = carat, y = price, color= clarity, label = color, shape = cut))+
  geom_point( size =1)+
  geom_text(aes(label = ifelse(carat<1.2, as.character(color), '')), hjust=0, vjust=0)+
  ggtitle("[Price per Carat]")+
  xlab("carat")+
  ylab("price")+
  theme(text=element_text(size=25, family="Blanche de la Fontaine"), panel.background =element_rect("darkolivegreen"))+
  scale_colour_brewer(palette = "Set1")
print(uglyplot)

  
```

